Non-kissing and non-crossing complexes \\ for locally gentle algebras

### 2018-07-04 draft/accordionComplexSurfaces.tex
relabel theorems according to sections
Minor changes.

\begin{definition}
\label{def:curveOfAWalk}
Let~$\omega = \ldots \alpha_{i-1}^{\varepsilon_{i-1}}\alpha_{i}^{\varepsilon_i}\alpha_{i+1}^{\varepsilon_{i+1}}$ be a (possibly infinite) walk on~$\bar Q$. 
Define the curve~$\curveof(\omega)$ to be the concatenation of the curves~$\curveof(\alpha_i{\varepsilon_{i}})$ of Definition \ref{def:curveOfAnArrow}.
\end{definition}

@@

\begin{proposition}
\label{lem:walks=arcs}
The maps~$\curveof(-)$ and~$\walk(-)$ induce mutually inverse bijections between the set of undirected walks on~$\bar Q$ and the set of~$\dissection_{\bar Q}$-accordions on~$\surface(\bar Q)$.
\end{proposition}

>>>>

\begin{definition}
\label{def:curveOfAWalk}
Let~$\omega = \ldots \alpha_{i-1}^{\varepsilon_{i-1}}\alpha_{i}^{\varepsilon_i}\alpha_{i+1}^{\varepsilon_{i+1}} \ldots$ be a (possibly infinite) walk on~$\bar Q$. 
Define the curve~$\curveof(\omega)$ to be the concatenation of the curves~$\curveof(\alpha_i{\varepsilon_{i}})$ of Definition \ref{def:curveOfAnArrow}.
\end{definition}

@@

\begin{proposition}
\label{prop:walks=arcs}
The maps~$\curveof(-)$ and~$\walk(-)$ induce mutually inverse bijections between the set of undirected walks on~$\bar Q$ and the set of~$\dissection_{\bar Q}$-accordions on~$\surface(\bar Q)$.
\end{proposition}
